Supporting Information:\\ NMRlipids IV: Headgroup \& glycerol backbone structures, and cation binding in bilayers with PE and PG lipids

### 2021-03-23 manuscriptPGPEsuppl.tex

      POPE  & CHARMM36ua \cite{??}         &0       & 336	& 15254 &0    & 310  & 2$\times$200 & 2$\times$100 & \cite{charmm36uaPOPEfiles}  \\

@@

      POPE  & Berger-Vries \cite{??}       &0    & 128	& 3552  &0    & 303  & 2$\times$200 & 2$\times$100 & \cite{bergerPOPEfiles}  \\
      POPE  & Berger-largeH \cite{??}      &0    & 128	& 3552  &0    & 303  & 2$\times$200 & 2$\times$100 & \cite{berger2POPEfiles}  \\
%      DOPE  & Berger-Vries \cite{??}       &0    & 128	& 4789  &0    & 271  & 2$\times$200 & 2$\times$100 & \cite{bergerDOPEfiles}  \\
%      DOPE  & Berger-largeH \cite{??}      &0    & 128	& 4789  &0    & 271  & 2$\times$300 & 2$\times$100 & \cite{berger2DOPEfiles} \\ 

@@

      POPE             & LIPID17 \cite{gould18} & 0      & 500 & 25000 & 50  &  310  & 500 & 100 & \cite{POPElipid17} \\
%      POPE             & LIPID17 \cite{gould18} & 0.11   & 500 & 25000 & 50  &  310  & 500 & 100 & \cite{POPElipid17150mMNaCl} \\

@@

\noindent {\it POPE} Data is available at \cite{bergerPOPEfiles,berger2POPEfiles}. \todo{Simulation details by  T. Piggot.}

@@

\noindent {\it POPE} Data is available at \cite{gromosCKPpope}. \todo{Simulation details by  T. Piggot.}

>>>>

      POPE  & CHARMM36-UA \cite{??}         &0       & 336	& 15254 &0    & 310  & 2$\times$200 & 2$\times$100 & \cite{charmm36uaPOPEfiles}  \\

@@

      POPE  & Berger-POPE-2004 \cite{??}       &0    & 128	& 3552  &0    & 303  & 2$\times$200 & 2$\times$100 & \cite{bergerPOPEfiles}  \\
      POPE  & Berger-POPE-2018 \cite{??}      &0    & 128	& 3552  &0    & 303  & 2$\times$200 & 2$\times$100 & \cite{berger2POPEfiles}  \\
%      DOPE  & Berger-POPE-2004 \cite{??}       &0    & 128	& 4789  &0    & 271  & 2$\times$200 & 2$\times$100 & \cite{bergerDOPEfiles}  \\
%      DOPE  & Berger-POPE-2018 \cite{??}      &0    & 128	& 4789  &0    & 271  & 2$\times$300 & 2$\times$100 & \cite{berger2DOPEfiles} \\ 

@@

      POPE             & Lipid17 \cite{gould18} & 0      & 500 & 25000 & 50  &  310  & 500 & 100 & \cite{POPElipid17} \\
%      POPE             & Lipid17 \cite{gould18} & 0.11   & 500 & 25000 & 50  &  310  & 500 & 100 & \cite{POPElipid17150mMNaCl} \\

@@

Following the earlier convention in the NMRlipids Project~\cite{botan15}, 
for the Berger-based models we use the following naming convention: 
Berger - \{{\it molecule name}\} - \{{\it year when model published first time}\} \{{\it citation}\}.
%The reason is that there are several different molecular topologies which are using the non-bonded parameters originally
%developed by Berger et al.~\cite{berger97}. Thus the common factor in the Berger based models are the non-bonded parameters,
%while the molecule specific parameters might somewhat vary. However, the majority of the molecular level topologies are 
%relying (especially for the glycerol backbone and headgroup) on the parameters originally introduced by Marrink et al.~\cite{marrink98}.

\noindent {\it POPE} Data are available at Ref.~\citenum{bergerPOPEfiles} for Berger-POPE-2004~\cite{??} and at Ref.~\citenum{berger2POPEfiles} for Berger-POPE-2018~\cite{??}. \todo{Simulation details by  T. Piggot.}

@@

\noindent {\it POPE} Data is available at \cite{gromosCKPpopeT310}. \todo{Simulation details by  A. Peon.}
